
% -------------------------------------------------------
%  English Abstract
% -------------------------------------------------------


\pagestyle{empty}

\begin{latin}

\begin{center}
\textbf{Abstract}
\end{center}
\baselineskip=.8\baselineskip

The $k$-center problem---covering a set of points using $k$ congruent balls with minimum radius---is a well-known clustering model in computer science with a wide range of applications. The $k$-center is a well known NP-Hard problem. In this thesis, we focus on the $k$-center problem with outliers in high dimensional data streams. Due to increase in data size, we focus on the data stream model of the problem. Moreover, in real-world applications, where input points are noisy, it is very important to consider outliers.

In this thesis, we study $1$-center and $2$-center with outliers in high dimensional data streams in Euclidean space. We provide a $1.7$-approximation streaming algorithm for $1$-center with $z$ outliers (for constant $z$), which improves previous $1.73$-approximation algorithm. We also provide a $(1.8 + \epsilon)$-approximation streaming algorithm for $2$-center problem with outliers, improving upon the previous $(4 + \epsilon)$-approximation algorithm available for the problem. The space complexity and update time of both algorithms are $\text{poly}(z, d, \frac{1}{\epsilon})$, independent of the size of the stream.

\bigskip\noindent\textbf{Keywords}:
Clustering, $k$-Center, Streaming Data, Approximation Algorithm

\end{latin}

\newpage
